### 2013-10-04 Rcode/intro.rmd
improved package installation

Load in some functions.
```{r}
setwd("~/Documents/git/ash/Rcode/")
set.seed(32327)
## load Poisson_binomial and ash functions 
source("../Rcode/ash.R") 
library("qvalue")
```

>>>>

Load in some functions.
```{r}
setwd("~/Documents/git/ash/Rcode/")
set.seed(32327)
## load Poisson_binomial and ash functions 
source("../Rcode/ash.R") 
source("../Rcode/mix.R") 
library("qvalue")
```

### 2013-10-04 Rcode/test.mix.Rmd
improved package installation

################################# TESTING #####################################
```{r}
source("mix.R")
library("testthat")
temp = normalmix(c(0.5,0.5),c(-3,2),c(1,1))

expect_that(comp_mean(temp),equals(c(-3,2)))
expect_that(mixmean(temp),equals(-0.5))
expect_that(mixsd(temp),equals(2.692582))

>>>>

################################# TESTING #####################################
```{r}
setwd("~/Documents/git/ash/")
source("Rcode/mix.R")
source("Rcode/ash.R")
source("Rcode/ash.oldfuncs.R")
library("testthat")
temp = normalmix(c(0.5,0.5),c(0,0),c(1,2))

expect_that(comp_mean(temp),equals(c(0,0)))
expect_that(mixmean(temp),equals(0))
expect_that(mixsd(temp),equals(sqrt(2.5)))

comp_postmean(temp,0,1)
comp_postsd(temp,0,1)
postsd(temp,0,1)

set.seed(100)
beta = rnorm(100)
betahatse = abs(rnorm(100))
betahat = rnorm(100, beta,betahatse)

pd= posterior_dist(temp,betahat,betahatse)
mv=normmix.mv(pd)
expect_that(mv$mean,equals(postmean(temp,betahat,betahatse)))
expect_that(sqrt(mv$var),equals(postsd(temp,betahat,betahatse)))
